Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-03 paper/ms.tex
updated references, removed Hayashino 2004

\begin{enumerate}
\item The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
field has been known to harbor a region with a large density excess of
galaxies. {\bf The first sub-field of is taken around the same region
  observed in \cite{Hayashino2004}.}

@@

{\bf A secondary benchmark is the angular correlation function
(ACF). \cite{Yamada2012} does not report an ACF measurement for
  their fields. Instead we use the results by   \cite{Ouchi2008} who
  reported the ACF is over a region of $1$ deg$^2$ over the SXDS
  field.  We also keep track of the results by \cite{Hayashino2004}
  who reported the ACF in the SSA22 region, including its densest
  sub-field.}

{\bf There are some differences between \cite{Ouchi2008} observations
  and those by \cite{Yamada2012}. The details in the color selection,
  corresponding limiting luminosities and EW thresholds are different
  in these references. The average LAEs number density inferred by
  \cite{Hayashino2004} is  $0.37$ arcmin$^{-2}$, which is $30\%$
  higher than the new measurement by \cite{Yamada2012}. In the case of
  \cite{Ouchi2008} the number density is $0.10$ arcmin$^{-2}$, which
  is $\sim 50\%$ lower than the value inferred by \cite{Yamada2012}
  for a portion of the same region.}

@@

{\bf Therefore, using the whole SSA22 region as a benchmark in the
  number density distribution does not impose any bias. However, on
  has to  keep in mind that is not plausible that the full number
  density distribution from a simulation will include a very dense
  field. We do not require the presence of such field to judge a mock
  distribution as successful. The statistical test we perform to
  compare mock distributions   against   observations does not require
  such a perfect match.

  In terms of the ACF the results that include the densest
  field in SSA22 \citep{Hayashino2004} are consistent, within 
  uncertainties, with the results of other fields
  \citep{Ouchi2008}. In spite of this consistency we will focus on the
  results from \citep{Ouchi2008}.}

@@

The right panel in Figure \ref{fig:halos} shows the  integrated dark matter halo surface
density as a function of  minimum halo mass $M_{\rm min}$. Each line
corresponds to one of the 210 sub-volumes in the Bolshoi
simulation. The gray band indicates the surface density values for
LAEs allowed by observations \citep{Yamada2012}. The dashed lines
represent the average values in the fields observed by
\citep{Hayashino2004,Ouchi08}.

@@

{\bf A fourth caveat is the comparing results for the number density
  statistics and the ACF from surveys with different EW cuts. In this
  sense we highlight againt that the two filters and selection
  criteria used by \citep{Ouchi2008} and \citep{Yamada2012} are only
  slightly different. The number densities in the general fields by
  \citep{Yamada2012} is $0.083\pm0.004$ arcmin$^{-2}$, while in
  \citep{Ouchi2008} is $0.099\pm0.005$ arcmin$^{-2}$. This gives us
  confidence that the two different samples can give a self-consistent
  picture for our studies.}

>>>>

\begin{enumerate}
\item The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
field has been known to harbor a region with a large density excess of
galaxies.

@@

{\bf A secondary benchmark is the angular correlation function
(ACF). \cite{Yamada2012} does not report an ACF measurement for
  their fields. Instead we use the results by   \cite{Ouchi2008} who
  reported the ACF is over a region of $1$ deg$^2$ over the SXDS
  field.  }

{\bf There are some differences between \cite{Ouchi2008} observations
  and those by \cite{Yamada2012}. The details in the color selection,
  corresponding limiting luminosities and EW thresholds are different
  in these references. In the case of
  \cite{Ouchi2008} the number density is $0.099\pm0.005$ arcmin$^{-2}$, which
  is 50\% lower that the median value of $0.20$ arcmin$^{-2}$ for the
  the general fields in \cite{Yamada2012}}

@@

{\bf Therefore, using the whole SSA22 region as a benchmark in the
  number density distribution does not impose any bias. However, on
  has to  keep in mind that is not plausible that the full number
  density distribution from a simulation will include a very dense
  field. We do not require the presence of such field to judge a mock
  distribution as successful. The statistical test we perform to
  compare mock distributions   against   observations does not require
  such a perfect match. }

@@

The right panel in Figure \ref{fig:halos} shows the  integrated dark matter halo surface
density as a function of  minimum halo mass $M_{\rm min}$. Each line
corresponds to one of the 210 sub-volumes in the Bolshoi
simulation. The gray band indicates the surface density values for
LAEs allowed by observations \citep{Yamada2012}. The dashed lines
represent the average values in the fields observed by
\citep{Ouchi2008}.

@@

{\bf A fourth caveat is the comparing results for the number density
  statistics and the ACF from surveys with different EW cuts. In this
  sense we highlight againt that the two filters and selection
  criteria used by \citep{Ouchi2008} and \citep{Yamada2012} are only
  slightly different. The median number density in the general fields by
  \citep{Yamada2012} is $0.20$ arcmin$^{-2}$, while in
  \citep{Ouchi2008} is $0.099\pm0.005$ arcmin$^{-2}$. This gives us
  confidence that the two different samples can give a self-consistent picture
  within a factor of $\sim2$ for our studies.}
